Titeln på avhandlingens språk

### 2022-11-19 body/part1/overview.tex
contrib

>>>>

This thesis presents seven key contributions to the literature; these are summarized below:

\begin{enumerate}
    \item\label{item:contrib:methodology} A methodological approach to studying system responsiveness versus resource consumption trade-offs in \ac{WCA}.
    This approach is based on the emulation of the client-side workload, while maintaining the \emph{real} server-side process as well as network stack.
    \item In conjunction with the aforementioned methodology, a tool (EdgeDroid) for the emulation of human behavior in \ac{WCA}.
    This tool implements the first ever parametrizable model of human behavior for these applications using empirical data collected from a series of human-subject experiments.
    \item A characterization of the effects of individual personality differences in human responses to reduced system responsiveness in interactive systems such as \acl{WCA}.
    In particular, this thesis presents novel evidence for the modulating properties of \emph{neuroticism} on the reaction to increased delay in these systems.
    \item An preliminary, yet novel exploration of the implications of realistic modeling of human timings in \ac{WCA} applications for their optimization potential.
    \item\label{item:contrib:methodology:ncs} An extension of the methodology described in \cref{item:contrib:methodology} towards \ac{NCS}.
    \item A novel tool, CLEAVE, for the emulation of \ac{NCS} on edge infrastructure.
    This tool has been designed from the ground-up to be edge-native, implemented using widely-adopted technologies in the disciplines of cloud and edge computing.
    \item Finally, a software framework for the management and automation of the testbeds required for the methodology described in \cref{item:contrib:methodology,item:contrib:methodology:ncs}.
\end{enumerate}
